---
title: "Extracting data from MEX files"
author: "Michał Bojanowski"
date: "`r Sys.Date()`"
output:
  github_document:
    toc: true
editor_options: 
  chunk_output_type: console
---


```{r setup, cache=FALSE, include=FALSE}
suppressPackageStartupMessages({
  library(maxqdar)
  library(dplyr)
  library(tidyr)
})

knitr::opts_chunk$set(
  cache=TRUE,
  echo=TRUE
)
```



# Read data

Directories (unzipped files from Agata)

```{r dirs}
dirs <- c(
  "Documents 100-300 (without Portuguese letters)",
  "WSZYSTKIE"
)
```

File name database

```{r files}
files <- 
lapply(
  dirs,
  function(d) {
    data_frame(
      mex_dir=d, 
      mex_file=list.files(d)
      )
  }
) %>%
  bind_rows() %>%
  mutate(
    mex_path = file.path(mex_dir, mex_file)
  )
```


# Extract

```{r extract-mex}
train <-
files %>%
  mutate(
    data = lapply(files$mex_path, extract_mex_codings)
  ) %>%
  unnest(data) 
```

And thus we have

```{r}
glimpse(train)
```



# Bad file names

Catching MEX files that do not have proper file names. These popped-up because some of the coders did not import the source files, but pasted their content directly into MAXQDA. In consequence, we lost the connection between file name and its content.

```{r bad-file-names}
bf <-
train %>%
  extract(
    file_name,
    into = c("bf_word", "bf_id"),
    regex = "^([A-Za-z]+) \\(([0-9]+)\\)",
    remove = FALSE
  ) %>%
  mutate(
    bf_is = !is.na(bf_word) | is.na(file_name),
    bf_id = as.numeric(bf_id)
  )
```

Number of text fragments that do or do not have proper file name, per MEX file. "Bad" fragments cannot be (easily) matched with full text.

```{r bf-table, R.options=list(knitr.kable.NA="-")}
z <-
bf %>%
  mutate(
    ok = ifelse(bf_is, "bad", "good")
  )

z %>%
  count(mex_file, ok) %>%
  spread(ok, n) %>%
  knitr::kable()

z %>%
  count(ok) %>%
  knitr::kable()
```


```{r eval=FALSE, include=FALSE}
# checking 
bf %>%
  filter(mex_file == "12 - wszystko - Esther exchange.mex") %>%
  pull(file_name)
```



























# Save as CSV

```{r write-csv, eval=FALSE}
readr::write_csv(train, "training_data.csv")
```
